\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2020-03-11 paper/supporting_information.tex
editing supplement [WIP, does not compile]
backing up progress [WIP]

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_2}
\caption{\textbf{Reconstruction quality for Dataset 2, Experiments 1
    and 2.}  \textbf{A. Distributions of correlations between observed
    versus reconstructed activity by electrode, for Dataset 2
    (Experiment 1).}  The plots are in the same format as
  Figure~\ref{fig:supplemental_1}B, but reflect data only from
  Experiment 1 in Dataset 2.  \textbf{A. Distributions of correlations between observed
    versus reconstructed activity by electrode, for Dataset 2
    (Experiment 2).  The plots are in the same format as Panel A, but
    reflect data only from Experiment 2 in Dataset 2.}} 
\label{fig:supplemental_2}
\end{figure}

%JRM STOPPED HERE
\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\textbf{Reconstruction quality across all electrodes, broken
    down by Dataset 2 experiment.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Dataset 1.}  The across-patient distribution (black) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (gray)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode.
    \textbf{B. Distributions of correlations for Dataset 2.}  This
    panel is in the same format as Panel A, but reflects results
    obtained from Dataset 2.  The histograms aggregate data across
    both Dataset 2 experiments; for results broken down by experiment
    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
      performance by location.} The colors denote the average across-session
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface~\citep{CombEtal19}.}

\caption{\textbf{Reconstruction quality across all electrodes in two
      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
    in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
 \textbf{B. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 2.}  Same format as Figure~3A and B, but reflects
    data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
    plot).  \textbf{C.--D.  Reconstruction
      performance by location.} Each dot reflects the location of a
    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
    average within-experiment (across-session)
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface~\citep{CombEtal19}.}
\label{fig:supplemental_3}
\end{figure}

>>>>

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_2}
\caption{\textbf{Reconstruction quality for Dataset 2, Experiments 1
    and 2.}  \textbf{A. Distributions of correlations between observed
    versus reconstructed activity by electrode, for Dataset 2
    (Experiment 1).}  The plots are in the same format as
  Figure~\ref{fig:supplemental_1}B, but reflect data only from
  Experiment 1 in Dataset 2.  \textbf{A. Distributions of correlations between observed
    versus reconstructed activity by electrode, for Dataset 2
    (Experiment 2).  The plots are in the same format as Panel A, but
    reflect data only from Experiment 2 in Dataset 2.}}
% \label{fig:supplemental_2}
% \end{figure}
%
% %JRM STOPPED HERE
% \begin{figure}[p]
% \centering
% \includegraphics[width=\textwidth]{figs/supplemental_3}
% \caption{\textbf{Reconstruction quality across all electrodes, broken
%     down by Dataset 2 experiment.}  \textbf{A. Distributions of correlations
%       between observed versus reconstructed activity by electrode, for
%       Dataset 1.}  The across-patient distribution (black) reflects
%     reconstruction accuracy (correlation) using a correlation model
%     learned from all but one patient's data, and then applied to that
%     held-out patient's data.  The within-patient distribution (gray)
%     reflects performance using a correlation model learned from the same
%     patient who contributed the to-be-reconstructed electrode.
%     \textbf{B. Distributions of correlations for Dataset 2.}  This
%     panel is in the same format as Panel A, but reflects results
%     obtained from Dataset 2.  The histograms aggregate data across
%     both Dataset 2 experiments; for results broken down by experiment
%     see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
%       performance by location.} The colors denote the average across-session
%     correlation, using the across-patient correlation model, between
%     the observed and reconstructed activity at the given electrode
%     location projected to the cortical surface~\citep{CombEtal19}.}
%
%
% \caption{\textbf{Reconstruction quality across all electrodes in two
%       Dataset 2 experiments.}  \textbf{A. Distributions of correlations
%       between observed versus reconstructed activity by electrode, for
%       Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
%     in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
%  \textbf{B. Distributions of correlations
%       between observed versus reconstructed activity by electrode, for
%       Experiment 2.}  Same format as Figure~3A and B, but reflects
%     data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
%     plot).  \textbf{C.--D.  Reconstruction
%       performance by location.} Each dot reflects the location of a
%     single implanted electrode from Dataset 2, Experiment 1 (Panel C)
%     or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
%     average within-experiment (across-session)
%     correlation, using the across-patient correlation model, between
%     the observed and reconstructed activity at the given electrode
%     location projected to the cortical surface~\citep{CombEtal19}.}
\label{fig:supplemental_3}
\end{figure}
